---
title: "Protocol for Library Prep: Bacterial Genome using LSK114 on MinION"
author: "Alicia M. Rich, Ph.D."
date: "`r Sys.Date()`"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
runtime: shiny
params:
  local: "/Users/aliciamrich/RStudioMacbook/GitRepos/richlab_main/"
  laptop: "/Users/aliciamrich/RStudioMacbook/GitRepos/richlab_main/"
  desktop: "/Users/arich/Library/CloudStorage/GoogleDrive-aliciamrich@gmail.com/Other computers/My MacBook Pro/RStudioMacbook/GitRepos/richlab_main/"
  
---

```{r global, include=F}
params <- list(
  local = "/Users/aliciamrich/RStudioMacbook/GitRepos/richlab_main/",
  laptop = "/Users/aliciamrich/RStudioMacbook/GitRepos/richlab_main/",
  desktop = "/Users/arich/Library/CloudStorage/GoogleDrive-aliciamrich@gmail.com/Other computers/My MacBook Pro/RStudioMacbook/GitRepos/richlab_main/"
)

source(paste0(params$local, "dependencies/setup.R"))
opts_chunk$set(message = FALSE,
               warning = FALSE,
               echo    = FALSE,
               include = TRUE,
               eval    = TRUE)
source(paste0(params$local, "protocols/builds/Build_Protocol_SQK_LSK114.R"))
```

# Overview

## Row

### Equipment, Materials, and Consumables 

```{r}
card(full_screen = T,
     card_body(gt_output(outputId = "supplies_all")))
```


```{r, context = "server"}
output$supplies_all <- render_gt(expr = gt_supplies)
```

# DNA Repair and End Prep {.tabset .tabset-fade}

## Materials

```{r}
card(full_screen = T,
     card_body(gt_output(outputId = "supplies_endprep")))
```

```{r, context = "server"}
output$supplies_endprep  <- render_gt(expr = supplies_endprep)
```

## Procedure

(@) Thaw DNA Control Sample (DCS) at room temperature, spin down, mix by pipetting, and place on ice.

## Notes

# Adapter Ligation {.tabset .tabset-fade}

## Materials

```{r}
card(full_screen = T,
     card_body(gt_output(outputId = "supplies_adapter")))
```

```{r, context = "server"}
output$supplies_adapter  <- render_gt(expr = supplies_adapter)
```



# Library Clean-up

# Prime and Load the Flow Cell {.tabset .tabset-fade}

## Materials

```{r}
card(full_screen = T,
     card_body(gt_output(outputId = "supplies_flowcell")))
```

```{r, context = "server"}
output$supplies_flowcell  <- render_gt(expr = supplies_flowcell)
```




      paste0(ymd_hms(now(), tz = Sys.timezone()))
